\PassOptionsToPackage{svgnames}{xcolor}
\documentclass[10pt,letterpaper]{article}
\usepackage[top=.25in, bottom=.5in, left=.5in, right=.5in]{geometry}
\usepackage{tcolorbox}
\usepackage{lipsum}
\tcbuselibrary{skins,breakable}
\usetikzlibrary{shadings,shadows}

\usepackage{graphicx} % Allows to include images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

\usepackage{multicol}
\usepackage{float}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{hyperref}

\title{Practice 4: Iron Curtain Defense}
\author{}
\date{}

\newenvironment{agendablock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGray,colframe=DarkGray,%
    colbacklower=Gray!75!LightGray,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{evenBlock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGreen,colframe=DarkGreen,%
    colbacklower=LimeGreen!75!LightGreen,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{oddBlock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightBlue,colframe=DarkBlue,%
    colbacklower=DarkBlue!75!LightBlue,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myexampleblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGreen,colframe=DarkGreen,%
    colbacklower=LimeGreen!75!LightGreen,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myalertblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightCoral,colframe=DarkRed,%
    colbacklower=Tomato!75!LightCoral,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightBlue,colframe=DarkBlue,%
    colbacklower=DarkBlue!75!LightBlue,%
    title=#1]}%
    {\endtcolorbox}

\usepackage{lmodern}

\begin{document}
\fontfamily{lmss}\selectfont
\maketitle

\begin{agendablock}{Practice Activities}
    Dribbling and Ball Control at your feet is another key skill.  The ability to dribble well allows you to find open space to pass or shoot. 
    \begin{enumerate}
        \item Warm ups / Coerver Touches [ 15 min ]
        \item Agility Runs [ 24 min ]
        \item Defensive Drills [ 18 min ]
        \item Game Situational Drills [ 15 min ]
        \item Small Sided Game [ 15 min ]
    \end{enumerate}
\end{agendablock}

\input{../Warmups}

\clearpage



\section{Agility Runs}
\href{https://www.youtube.com/watch?v=3ew2m3m5f0M}{Agility Runs} () (10 min)
Defenders and forwards needs to be agile, stop and go hard, these exercises will work on speed and agility.

\textbf{Time: 8 minutes}
\input{../Drills/Drill_DeaccelShuddle}

\textbf{Time: 8 minutes}
\input{../Drills/Drill_LateralShuddle}

\textbf{Time: 8 minutes}
\input{../Drills/Drill_Crosshairs}

\clearpage

\section{Drills}

\textbf{Time: 8 minutes}
\begin{evenBlock}{Back-Petal}
Instruct how to move backward and apply pressure.

\textbf{Goal for the Drill:}

For the Defender to learn how to effectively back-petal to keep pressure on the attacker but not allow him to pass the defender.


\textbf{How:}

Create a 10 yard box.  The attacker starts at one box edge and dribbles out the other box edge, but trys to get past the defender.  The attacker can't dribble out the sides of the box.

The defender back petals trying to keep the attacker in front of him and not letting him get past him.  The defender should try to force the attacker to the edges of the box.

The defender does not try to steal or block the ball - focus on the attacker.

Switch roles, then rotate around.  So players can be attackers and defenders against the other players.

\textbf{Coaching Points:}
\begin{itemize}
    \item Staggered stance with toes at a 45 degree angle.
    \item Bent knees with weight on the balls of the feet.
    \item Chest leaning over the toes.
    \item Low center of gravity for greater explosion/quick change of direction (upright takes longer to start).
    \item Ability to shuffle quickly.
    \item Shuffle backward  angling your body to force them one direction or the other.  This simulates pushing them away from center of the field (away from our the goal).
\end{itemize}

\end{evenBlock}

\textbf{Time: 10 minutes}
\begin{evenBlock}{Box Defending}
Create a 10 yard box.  The defender (D1) starts within the box, and a second player the attacker (A1) attempts to dribble past the defender to the other side of the box.

If A1 dribbles the ball out the far end - he wins and the defender stays in the box and trys to defend the next attacker.

If D1 is able to take control or kick the ball out of the sides of the box - he wins.
Then A1 becomes the defender and D1 goes to the back of Attacking Line.

Once a player wins the next attacker trys to get through.  This makes the defender transition quickly.

\textbf{When defending 1v1’s in soccer it is very important to focus on the following key elements}:
\begin{itemize}
\item Staggered stance with toes at a 45 degree angle.
\item Bent knees with weight on the balls of the feet.
\item Chest leaning over the toes.
\item Low center of gravity for greater explosion/quick change of direction (upright takes longer to start).
\item Ability to shuffle quickly.
\item Pay attention to the distance of pressure (depends on speed of attacker vs. the speed of the defender) usually 1-3 yards
\item Remember that the player closest to the attacker should be the player pressuring the ball. Players should sprint to close down space as quickly as they can, then when they get 5 yards from the attacker they should slow down and take steps backwards to match the pace of the attacker. During this time, the defender should slowly close down the space between the attacker and defender. Often proper pressure will cause the attacker to lose the ball.

One way to have players recall the proper way to defend is by the term “Quick, Slow, Sideways, Low”.
\end{itemize}
\end{evenBlock}


%\input{../Drills/Drill_Foot_Soldiers}

\clearpage
\section{Game Situational Practice}

\textbf{Time: 15 minutes}
\input{../Drills/Drill_Secure_The_Box}

%\input{../Drills/Drill_2V1_Offense}

\section{Game Time}

\textbf{Time: 15 minutes}

\begin{evenBlock}{Small Sided Game}
    
    \textbf{Recap Positioning from P1}

    \textbf{With the Ball:}
    
    \begin{itemize}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \item Funnel Positioning.
        \item Go outside on our defensive half.
        \item Pass quickly down sidelines or into open space.
        \item Avoid passing backward.
        \item Make a pass early or move early.
    \end{itemize}
    \textbf{Without the Ball:}
    \begin{itemize}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \item Funnel Positioning - know your position, repeat it in your head.
        \item Move to open space - ask yourself, if I had the ball could I pass the ball to the person who has the ball?  If the answer is no, then move so you can make that pass to the person with the ball.
        \item Look and memorize your surroundings.
        \item Always be thinking what you want to do with the ball if you get the ball - this will help you make the correct play early.
        \item Make a pass early or move early.
    \end{itemize}
\end{evenBlock}

\begin{oddBlock}{Small Sided Game}
\end{oddBlock}

\section{Close}

NO SPRINTS!!!!

\end{document}