\PassOptionsToPackage{svgnames}{xcolor}
\documentclass[10pt,letterpaper]{article}
\usepackage[top=.5in, bottom=.75in, left=.5in, right=.5in]{geometry}
\usepackage{tcolorbox}
\usepackage{lipsum}
\tcbuselibrary{skins,breakable}
\usetikzlibrary{shadings,shadows}

\usepackage{graphicx} % Allows to include images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

\usepackage{multicol}
\usepackage{float}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\title{\vspace{-.5in}Practice 3: Master Dribbling}
\author{\vspace{-.5in}}
\date{\vspace{-.5in}}

\newenvironment{agendablock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGray,colframe=Black,%
    colbacklower=Gray!75!LightGray,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{evenBlock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGreen,colframe=DarkGreen,%
    colbacklower=LimeGreen!75!LightGreen,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{oddBlock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightBlue,colframe=DarkBlue,%
    colbacklower=DarkBlue!75!LightBlue,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myexampleblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGreen,colframe=DarkGreen,%
    colbacklower=LimeGreen!75!LightGreen,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myalertblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightCoral,colframe=DarkRed,%
    colbacklower=Tomato!75!LightCoral,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightBlue,colframe=DarkBlue,%
    colbacklower=DarkBlue!75!LightBlue,%
    title=#1]}%
    {\endtcolorbox}

\begin{document}

\fontfamily{lmss}\selectfont

\maketitle

\begin{agendablock}{Practice Activities}
    Dribbling and Ball Control at your feet is another key skill.  The ability to dribble well allows you to find open space to pass or shoot. 
    \begin{enumerate}
        \item Warm ups / Coerver Touches, HowTo [ 20 min ]
        \item Drills [ 30 min ]
        \item Game Situational Drills [ 15 min ]
        \item Small Sided Game [ 20 min ]
        \item Sprints [ 5 min ]
    \end{enumerate}
\end{agendablock}

\section{Warm Ups}
Run the \textbf{GATE DRIBBLING} drill until everyone arrives and for a few minutes after.

\textbf{Time: 2 minutes}
\begin{oddBlock}{Gate Dribbling}
Setup 2-4 square areas about 6x6 yards.  Then add one of each colored gate to the squares (ideally 4 gates per square each a different color).  The cones for each gate should be about a yard apart.  The goal is to have the players dribble through the each colored gate in each zone once.  First one to complete all gate in each zone wins.
\end{oddBlock}

\textbf{Time: 3 minutes}
\begin{myalertblock}{Theme of the Practice}
    \textbf{Perfect Dribbling!}

    Importance of Dribbling:
    \begin{itemize}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \item Dribbling sets up everything.
        \item Creates space to pass.
        \item Creates space to shoot.
        \item No offsides.
        \item Can attract or freeze defenders to allow yuor teammates to find open space.
    \end{itemize}

    Issues with Dribbling:
    \begin{itemize}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \item Dribbling moves the ball slower than passing or running.
        \item Attracts defenders (can be a positive - see above).
    \end{itemize}

\end{myalertblock}

\textbf{Time: 10 minutes}
\input{../Warmups}

\section{HOWTO:}
\input{../Drills/HOWTO_Dribble}

\section{Drills}

\textbf{Time: 10 minutes}
\input{../Drills/Drill_Cone_Weave}

\textbf{Time: 10 minutes}
\begin{oddBlock}{Straight line dribbling at speed ( 10 min )}
    \textbf{Drill:}
    \begin{enumerate}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \item Use the outside of the foot or laces to push the ball forward 2-3 steps in front of you.
        \item Continue until half field then make a turn inside cut and back to the end line.
    \end{enumerate}
    \textbf{Coaching Points:}
    \begin{enumerate}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \item Go slow until and get used to the feel of dribbling this way.
        \item Increase speed as it begins to feel more natural.
        \item Focus on your touch and timing as you approach the lines and try to make that cut right on the line.
        \item Can you beat coach?
    \end{enumerate}
\end{oddBlock}

\textbf{Time: 10 minutes}
\input{../Drills/Drill_Gate_Dribbling}


\section{Game Situational Practice}
\textbf{Time: 15 minutes, Started by 6:20PM}
\input{../Drills/Drill_Endzone_Soccer_Dribble}

%\input{../Drills/Drill_Dribble_Endline_Cross}

%\input{../Drills/Drill_2V1_Offense}

\section{Game}

\begin{oddBlock}{Small Sided}
    \textbf{Start Time: 6:35 PM}
    \textbf{Time:} 10 minute halves.

    \textbf{Size:} 4v4 or 5v5.

    Express:
    \begin{itemize}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \item  remind them about the practice: dribble into open space,
        \item dribble to pull defenders away from teammates,
        \item Look to beat a defender and shoot or pass.
        \item Funnel Positioning.
        \item Go outside on our defensive half.
        \item Pass quickly down sidelines or into open space.
        \item Avoid passing backward.
        \item Make a pass early or move early.
    \end{itemize}

\end{oddBlock}

\section{Close}
\begin{oddBlock}{Sprints}
    Escalation sprints while dribbling, sprint dribble to 15 yards and back, 30 yards and back, 45 yards and back, then 60 yards and back.

    \vspace{12pt}
    
    Slowly dribble around the border of the 19 yard box to cool down.

\end{oddBlock}

\end{document}