\PassOptionsToPackage{svgnames}{xcolor}
\documentclass[10pt,letterpaper]{article}
\usepackage[top=.5in, bottom=.75in, left=.5in, right=.5in]{geometry}
\usepackage{tcolorbox}
\usepackage{lipsum}
\tcbuselibrary{skins,breakable}
\usetikzlibrary{shadings,shadows}

\usepackage{graphicx} % Allows to include images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

\usepackage{multicol}
\usepackage{float}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\title{\vspace{-.5in}First Team Parent Meeting}
\author{}
\date{}

\newenvironment{agendablock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGray,colframe=Black,%
    colbacklower=Gray!75!LightGray,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{evenBlock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGreen,colframe=DarkGreen,%
    colbacklower=LimeGreen!75!LightGreen,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{oddBlock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightBlue,colframe=DarkBlue,%
    colbacklower=DarkBlue!75!LightBlue,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myexampleblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGreen,colframe=DarkGreen,%
    colbacklower=LimeGreen!75!LightGreen,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myalertblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightCoral,colframe=DarkRed,%
    colbacklower=Tomato!75!LightCoral,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightBlue,colframe=DarkBlue,%
    colbacklower=DarkBlue!75!LightBlue,%
    title=#1]}%
    {\endtcolorbox}

\usepackage{lmodern}

\begin{document}
\fontfamily{lmss}\selectfont
\maketitle

\begin{agendablock}{Welcome}
    \begin{itemize}
        \item Welcome New and Old Faces.
        \item Introduce myself and Jim - express the need for another an assistant coach, especially as the game season approaches for as backup - its difficult to run a game without an assistant and league rules prevent help unless they are listed on the roster.
        \item Express the need for a manager.
    \end{itemize}
\end{agendablock}

\begin{agendablock}{Review Expectations of the Team and the Parents}
    \begin{itemize}
        \item \textbf{Work Hard:} come ready to give it 100\% all the time.  We all have bad days, but you will grow more by giving it your all on a bad day than on a good day.  \textbf{Boys:}  This is competitive soccer, its expected we come ready to work hard as a team so we can succeed as a team.
        \textbf{Parents:} I expect you to `help' your boy come prepared for practice.  This includes insuring his nutrition and sleep needs are met. 
        \item \textbf{Honesty \& Integrity:} Be honest and follow through on what you say you are going to do or promise.  If you do, nobody will question you and nobody will fault you when outcomes do not turn out as you expected because they will know you did everything you tried to do.
        \item \textbf{Sportsmanship:}
        \begin{itemize}
            \item Discuss that this is team sport, there is no individual failure, we win and lose as a team.
            \item Support each other, encourage each other and help each other.
            \item We also help and respect the other team.
        \end{itemize}
        \item \textbf{Positive Attitudes:}
        \begin{itemize}
            \item Do not spread negativity - it impacts everyone.
            \item You don't need to be happy, but do not bring complaint or give up, stay positive and strive to learn from both good and bad outcomes.
        \end{itemize}  
        \item \textbf{Listen and Respect:} everyone needs to be listening when a coach, the manager or a referee is talking to the team and give your respect to coaches, the team manager, the referee and the fans.  Bad language or attitudes will not be tolerated.
        \item \textbf{Timeliness:} We have limited amounts of practice time and its important we arrive on time.  I encourage everyone to come early so we can start on time.  The first 14 practices are already planned out to the minute.
        On time means on the field with all equipment ready to play when everyone needs to be listening when a coach, the manager or a referee is talking to the team and give your respect to coaches, the team manager, the referee and the fans.  Bad language or attitudes will not be tolerated.
    \end{itemize}
\end{agendablock}

\clearpage

\begin{agendablock}{Goals for this year:}
    \begin{itemize}
        \item \textbf{Build Leaders and Sportsman:}  Learn leadership and sportsmanship.  A captain will be assigned for each practice - they lead the warm ups and are responsible for the team behaviors and ensuring water breaks are completed in a timely fashion.  Every game and scrimmage will have a new captain and the role rotates.
        \item \textbf{Perfect the Basic Skills:}  This really takes years but I expect major growth in the basics - passing, dribbling at speed and positioning.
        \item \textbf{Dedicated focus on Proper Defending Techniques.}
         \item \textbf{Dedicated focus on Ways to Beat a Defender.}
        \item \textbf{Learn 2-3 different overall game plan strategies.}
        \item \textbf{Perfect 1-2 set-piece strategies.}
        \item \textbf{Perfect defending the typical set-piece plays.}
    \end{itemize}
\end{agendablock}

\begin{agendablock}{Player Work Outside of Practice}
    \begin{itemize}
        \item \textbf{Stress importance of daily touches.}  I expect the boys to perform their touches at least 4 days a week (thats every non-practice day but one).
        \item \textbf{This FALL: Ball work for 10 minutes 4 days week - minimum.}  \textbf{To the Boys:} I can't stress enough how much growth you will see if that spending 10 minutes a day with the ball at your feet.  When winter comes the space and time are limited.  This fall is when you can make large strides in your soccer abilities.
        \item Our current skill set is a U8 premier player.  I want to get the team up to U10 premier level skill set before the end of the year.
        \item If the boys spend 10 minutes a day practicing with the ball at their feet we will be doing U10 or U12 premier drills by the end of the year.
        \item I can share links to videos for the boys to watch that will explain the same points I will cover in practice.
        \item Endurance: The field is large and our team is small.  I would encourage all the boys to try and do as much cardio activity as they can to prepare for the spring.  We will include endurance activities at each practice.  Come prepared.
    \end{itemize}
\end{agendablock}

\begin{agendablock}{Skill Building Encouragement and Leadership}
If your boy learns a new advanced skill on his own, such as a new Coerver move, or a move to beat a defender and can successfully demo it to me and is `prepared teach' how to do the move he can have 10 minutes of practice time to introduce that skill to the other boys.  If he learns to juggle or learns a new juggling move he can have 5 miinutes at the end of practice to demonstrate the skill.

Note as a bonus for the team - everyone gets out of sprints that day - unless the effort put forth in practice was poor and they earned double or triple sprints.
\end{agendablock}

\begin{agendablock}{Practice Variations}
Throughout the year our team and the other U11 travel team will pool together for a combined practice and/or scrimmage.

This fall this will occur on Tuesdays.  If its planned in advance I will send out notice.  Being that Tuesdays are I would also like to try and organize a scrimmage on a different time and date so the entire time could play.

\textbf{Guest Coaches:}
I am working on getting some guest coaches to help and or teach specialized instruction.  One area of special instruction might be strength and agility training.  If they happen I will plan them for the winter.  The availability of these coaches is greater in the winter months.
\end{agendablock}

\begin{agendablock}{Friendly Scrimmages}
We will try to schedule some friendlies this fall and this winter.

This is an area in which having a manager would be a great help - so please consider volunteering for this role.
Without one however I will do my best to try and find teams.

Last year a club from Syracuse came - so I assume they are planning on coming here again.  They always bring good talent so we need to focus hard now to be ready.
\end{agendablock}

\begin{evenBlock}{U10 vs U11 Rule Changes}
    \begin{itemize}
        \item Larger field.
        \item Goal Keeper punts are now allowed.
        \item No retreat to half field.
        \item Offsides (explain this for the new boys).
        \item Throw-ins.
        \item 9 players not 7.
    \end{itemize}
\end{evenBlock}

\begin{evenBlock}{Communication Preferences}
    
    \textbf{TeamSnap:}

    TeamSnap will be the primary tool I use update you with upcoming practices, scrimmages and games.  It's also a tool that you can easily note which events your child is available for and which ones he is not.  

    Please keep your child's availability up to  date.  Having this information a week or more in advance allows me to plan the practices and drills accordingly.  However one reason I choose this App over other options such as Shutterfly is that fact that the App works on the Android platform better than Shutterfly and I can see current availability right before practice.
    
    \textbf{Email:}
    
    You probably already know this but I am a big fan of email.  However I know and respect not everyone uses email to the extent that I do.  Feel free to email me with questions and other non-emergency concerns.

    \textbf{Emergency:}
    In the event of an emergency please call or text me.  If I don't answer text.  I rarely check voice mail any more.
\end{evenBlock}

\begin{agendablock}{Questions}
    
\end{agendablock}

\end{document}