\PassOptionsToPackage{svgnames}{xcolor}
\documentclass[10pt,letterpaper]{article}
\usepackage[top=.5in, bottom=.75in, left=.5in, right=.5in]{geometry}
\usepackage{tcolorbox}
\usepackage{lipsum}
\tcbuselibrary{skins,breakable}
\usetikzlibrary{shadings,shadows}

\usepackage{graphicx} % Allows to include images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

\usepackage{multicol}
\usepackage{float}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\title{\vspace{-.5in}Practice 2: Perfect Passing}
\author{\vspace{-.5in}}
\date{\vspace{-.5in}}

\newenvironment{agendablock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGray,colframe=Black,%
    colbacklower=Gray!75!LightGray,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{evenBlock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGreen,colframe=DarkGreen,%
    colbacklower=LimeGreen!75!LightGreen,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{oddBlock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightBlue,colframe=DarkBlue,%
    colbacklower=DarkBlue!75!LightBlue,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myexampleblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGreen,colframe=DarkGreen,%
    colbacklower=LimeGreen!75!LightGreen,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myalertblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightCoral,colframe=DarkRed,%
    colbacklower=Tomato!75!LightCoral,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightBlue,colframe=DarkBlue,%
    colbacklower=DarkBlue!75!LightBlue,%
    title=#1]}%
    {\endtcolorbox}

\usepackage{lmodern}

\begin{document}
\fontfamily{lmss}\selectfont


\maketitle

\begin{agendablock}{Practice Activities}
    \begin{enumerate}
        \item Warm ups / Coerver Touches [ 15 min ]
        \item Drills [ 35 min ]
        \item Small Sided Activity [ 15 min ]
        \item Small Sided Game [ 20 min ]
        \item Sprints [ 5 min ] 
    \end{enumerate}
\end{agendablock}

\section{Warm Ups}
Run the \textbf{CLOCKS} drill until everyone arrives and for a few minutes after.

\textbf{Time: 2 minutes}
\input{../Drills/Drill_Clocks}

\textbf{Time: 3 minutes}
\begin{myalertblock}{Theme of the Practice}
    \textbf{Elements of the Game!}

    \begin{itemize}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \item throw-ins
        \item corner kicks - offense
        \item corner kicks - defending
        \item direct kicks - defending
        \item direct kicks - taking
        \item keeper distribution: punt, throw, goal kick.
        \item kick off.
    \end{itemize}
\end{myalertblock}

\textbf{Time: 10 minutes}
\input{../Warmups}

\clearpage



\section{Throw Ins}
\textbf{Total Time: 15 minutes}

\textbf{Time: 4 minutes}
\begin{agendablock}{HOWTO: Basic Throw In:}
\begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}
    \item Both feet must be planted during the throw.
    \item Both hands must be on the ball.
    \item Ball must travel over and behind the throwers head.
\end{itemize}
\end{agendablock}

\begin{agendablock}{HOWTO: Deep Throw In:}
\begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}
    \item For a more deeper throw in the player should advance to the line,
    \item Plant one foot and drag the other keeping it in contact with the ground.
    \item Both hands must be on the ball.
    \item Ball must travel over and behind the throwers head.
\end{itemize}
\end{agendablock}

\textbf{Time: 5 minutes}
\begin{evenBlock}{Throw-In to Feet}

    Have the boys partner up.  Have one player stand out of bounds and thrown in to the other player about 3 to 5 yards away.  The throw should be directed to the feet of the field player.  The field player should trap the ball at his feet.

\end{evenBlock}

\textbf{Time: 5 minutes}
\begin{oddBlock}{Throw-In leading field player}

    Have the boys partner up.  Have one player stand out of bounds and thrown in to the other player about 3 to 5 yards away.  The field player should be standing with his body open don field.  The throw should be directed in front of the field player. The field  player should make a first touch toward goal.
\end{oddBlock}

\section{Corner Kicks - Defense}
Explain the meanings of `far post' and `near post'.
\textbf{Time: 15 minutes}
\begin{evenBlock}{Positions}
    Mid-Field Wings: At goal posts.  Near post player positioned out of the goal to cut off that near post ball.

    Far post marker inside goal marking that edge.

    Center backs marking goal side.

    Far post Fullback and center midfielder marks goal side.

    Near post fullback marks a man.

    Center Forward Near 18 corner to cut off any passes out and ready to counter attack.
\end{evenBlock}

Once setup Coach will kick a corner for the team to handle.  Switch sides of the field.

\section{Corner Kicks - Offense}
\textbf{Time: 15 minutes}
\begin{evenBlock}{Positions}
    Forward and wing Mid-Fielders lineup at the corner of the 18 yard box.

    Near post full back takes kick.

    Center mid-fielder and Far post full back line up between near post 18 yard line and side line. Center mid runs to the PK spot, full back hovers playing the ball.

    Center backs should be at half field, keeper at his 18 yard line or further out.
    
\end{evenBlock}

\clearpage

\section{Direct Kicks - Defense}
\textbf{Time: 15 minutes}
\begin{evenBlock}{Positions}
    Form a Wall as close to the kicker as possible- center forward, mid field wing(s).  Make the referee move you away from the kick.  Center turn and face the keeper and adjust left or right as directed.   

    Defenders mark goal side within the funnel.
\end{evenBlock}

\section{Direct Kicks - Offense}
\textbf{Time: 15 minutes}
\begin{evenBlock}{Positions}
    If the ball is in the 
\end{evenBlock}

\section{Small Sided Activity}
\textbf{Time: 15 minutes, Started at 1:15 PM to 1:20 PM}
\input{../Drills/Drill_Touchdown_Passing}

\section{Game}

\textbf{Start Time: 1:35 PM}

\begin{oddBlock}{Small Sided}
    \textbf{Time:} 10 minute halves.

    \textbf{Size:} 4v4 or 5v5.

    Express:
    \begin{itemize}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \item  remind them about the practice goals and expectation there is a lot of movement and passing.
        \item Funnel Positioning.
        \item Go outside on our defensive half.
        \item Pass quickly down sidelines or into open space.
        \item Avoid passing backward.
        \item Make a pass early or move early.
    \end{itemize}

\end{oddBlock}

\section{Close}
\begin{oddBlock}{Sprints (5 min)}
    Agility runs to cone 5 yards away, stop and step circling cone then explode to next cone, circling it then explode sprinting to half field, jog back to end line and repeat 3 times.
\end{oddBlock}

\end{document}