\PassOptionsToPackage{svgnames}{xcolor}
\documentclass[10pt,letterpaper]{article}
\usepackage[top=.5in, bottom=.75in, left=.5in, right=.5in]{geometry}
\usepackage{tcolorbox}
\usepackage{lipsum}
\tcbuselibrary{skins,breakable}
\usetikzlibrary{shadings,shadows}

\usepackage{graphicx} % Allows to include images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

\usepackage{multicol}
\usepackage{float}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\title{\vspace{-.5in}Practice 2: Perfect Passing}
\author{\vspace{-.5in}}
\date{\vspace{-.5in}}

\newenvironment{agendablock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGray,colframe=Black,%
    colbacklower=Gray!75!LightGray,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{evenBlock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGreen,colframe=DarkGreen,%
    colbacklower=LimeGreen!75!LightGreen,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{oddBlock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightBlue,colframe=DarkBlue,%
    colbacklower=DarkBlue!75!LightBlue,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myexampleblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightGreen,colframe=DarkGreen,%
    colbacklower=LimeGreen!75!LightGreen,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myalertblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightCoral,colframe=DarkRed,%
    colbacklower=Tomato!75!LightCoral,%
    title=#1]}%
    {\endtcolorbox}

\newenvironment{myblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightBlue,colframe=DarkBlue,%
    colbacklower=DarkBlue!75!LightBlue,%
    title=#1]}%
    {\endtcolorbox}

\usepackage{lmodern}

\begin{document}
\fontfamily{lmss}\selectfont


\maketitle

\begin{agendablock}{Practice Activities}
    \begin{enumerate}
        \item Warm ups / Coerver Touches [ 15 min ]
        \item Drills [ 50 min ]
        \item Recap positioning tactics from P1 [ 5 min ]
        \item Small Sided Game (Keep Away maybe) [ 15 min ]
        \item Sprints [ 5 min ] 
    \end{enumerate}
\end{agendablock}

\section{Warm Ups}
Run the \textbf{CLOCKS} drill until everyone arrives and for a few minutes after.

\textbf{Time: 2 minutes}
\input{../Drills/Drill_Clocks}

\textbf{Time: 3 minutes}
\begin{myalertblock}{Theme of the Practice}
    \textbf{Perfect Passing!}

    Importance of passing:
    \begin{itemize}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \item Explain passing is the most critical skill in soccer.
        \item Explain that soccer is a game of possession (a advanced game of keep away) above all else.
        \item Ask: `Can the opposing team score if they never get possession of the ball?'
        \item Passing can tire the opposing team.  A tired team makes more mistakes and will turn over the ball more often and give up more goals.
        \item Perfect passing is very hard because it requires 3 critical elements:
        \begin{itemize}
            \setlength{\itemsep}{0pt}
            \setlength{\parskip}{0pt}
            \setlength{\parsep}{0pt}
            \item a team member who is open,
            \item an accurate pass with the correct pace,
            \item a good first touch (using the correct foot).
        \end{itemize}
        \item We will practice all of these elements today starting with the accurate pass and first touch.
    \end{itemize}
\end{myalertblock}

\textbf{Time: 10 minutes}
\input{../Warmups}

\section{HOWTO:}
\input{../Drills/HOWTO_Pass}

\clearpage

\section{Drills}

The following drills are going to stress 4 things:
\begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}
    \item Perfecting our first touch.
    \item Practicing the correct foot to use for that first touch.
    \item Movement - always be move into a space which is a passing option.
    \item Strong, accurate, controllable passing.
\end{itemize}

\textbf{Time: 10 minutes}
\input{../Drills/Drill_Box_Passes}

\textbf{Time: 10 minutes}
\input{../Drills/Drill_4_Corner_Passing}

\clearpage

\textbf{Time: 10 minutes}
\input{../Drills/Drill_Triangle_Passing}

The following can be optional if time is running short.  Getting in the Small Sided activity and/or the Small Sided game should take precedence over the next drill at this practice.

\textbf{Time: 8 minutes}
\input{../Drills/Drill_Figure8_Passing}


\clearpage

\section{Small Sided Activity}
\textbf{Time: 15 minutes}
\input{../Drills/Drill_Touchdown_Passing}

\section{Game}

\begin{oddBlock}{Small Sided}
    \textbf{Time:} 10 minute halves.

    \textbf{Size:} 4v4 or 5v5.

    Express:
    \begin{itemize}
        \setlength{\itemsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \item  remind them about the practice goals and expectation there is a lot of movement and passing.
        \item Funnel Positioning.
        \item Go outside on our defensive half.
        \item Pass quickly down sidelines or into open space.
        \item Avoid passing backward.
        \item Make a pass early or move early.
    \end{itemize}

\end{oddBlock}

\section{Close}
\begin{oddBlock}{Sprints (5 min)}
    Agility runs to cone 5 yards away, stop and step circling cone then explode to next cone, circling it then explode sprinting to half field, jog back to end line and repeat 3 times.
\end{oddBlock}

\end{document}